### 2019-10-29 README.Rmd
catching up with tmle package changes

        @manual{hejazi2019methyvimbioc,
          author = {Hejazi, Nima S and {van der Laan}, Mark J},
          title = {{methyvim}: Targeted, robust, and model-free differential
            methylation analysis},
          doi = {10.18129/B9.bioc.methyvim},
          url = {https://bioconductor.org/packages/methyvim},
          note = {R package version 1.6.0}
        }

>>>>

        @manual{hejazi2019methyvimbioc,
          author = {Hejazi, Nima S and {van der Laan}, Mark J},
          title = {{methyvim}: Targeted, robust, and model-free differential
            methylation analysis},
          doi = {10.18129/B9.bioc.methyvim},
          url = {https://bioconductor.org/packages/methyvim},
          note = {R package version 1.8.0}
        }
